---
title: "Test2_R"
output: html_document
---


```{r}

#retrieve the abalone data
uciaddress <- "http://archive.ics.uci.edu/ml/machine-learning-databases/"
dataset <- "abalone/abalone.data"
getdataset <- paste(uciaddress, dataset, sep="")
abalone <- read.csv(getdataset)
str(abalone)

#add column names to the data set
colnames(abalone) <- c("Gender","Length","Diameter","Height","Whole_wgt","Shucked_wgt","Viscera wgt","Shell wgt","Rings")
str(abalone)
head(abalone)
dim(abalone)

#Question 1

#to pull sample from abalone data frame

n<-nrow(abalone)

absample1<-randomSample(abalone, n*.01, FALSE)
absample10<-randomSample(abalone, n*.10, FALSE)
absample25<-randomSample(abalone, n*.25, FALSE)
absample50<-randomSample(abalone, n*.5, FALSE)
absample80<-randomSample(abalone, n*.80, FALSE)
absample100<-randomSample(abalone, n, FALSE)

#to create a vector with the minimum, maximum, mean, and variance of the Whole Weight column in the abalone data set for each of the sample sizes
data1<-c(min(absample1$Whole_wgt), max(absample1$Whole_wgt), mean(absample1$Whole_wgt), var(absample1$Whole_wgt))
data10<-c(min(absample10$Whole_wgt), max(absample10$Whole_wgt), mean(absample10$Whole_wgt), var(absample10$Whole_wgt))
data25<-c(min(absample25$Whole_wgt), max(absample25$Whole_wgt), mean(absample25$Whole_wgt), var(absample25$Whole_wgt))
data50<-c(min(absample50$Whole_wgt), max(absample50$Whole_wgt), mean(absample50$Whole_wgt), var(absample50$Whole_wgt))
data80<-c(min(absample80$Whole_wgt), max(absample80$Whole_wgt), mean(absample80$Whole_wgt), var(absample80$Whole_wgt))
data100<-c(min(absample100$Whole_wgt), max(absample100$Whole_wgt), mean(absample100$Whole_wgt), var(absample100$Whole_wgt))

#to create a data frame with all of the variables created above
data_all<-data.frame(data1, data10, data25, data50, data80, data100)

#adding column and row names to our data frame
colnames(data_all)<-c("1%Sample", "10%Sample", "25%Sample", "50%Sample", "80%Sample", "100%Sample")
rownames(data_all)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance")

data_all

#Question 2
require(ggplot2)


#creating histograms with each of the sample sizes
sample_plot1<-ggplot(absample1, aes(x=absample1$Whole_wgt))
sample_plot1<- sample_plot1 + geom_histogram() + labs(x="1% Sample Size")
print(sample_plot1)
sample_plot10<-ggplot(absample10, aes(x=absample10$Whole_wgt))
sample_plot10<- sample_plot10 + geom_histogram() + labs(x="10% Sample Size")
print(sample_plot10)
sample_plot25<-ggplot(absample25, aes(x=absample25$Whole_wgt))
sample_plot25<- sample_plot25 + geom_histogram() + labs(x="25% Sample Size")
print(sample_plot25)
sample_plot50<-ggplot(absample50, aes(x=absample50$Whole_wgt))
sample_plot50<- sample_plot50 + geom_histogram() + labs(x="50% Sample Size")
print(sample_plot50)
sample_plot80<-ggplot(absample80, aes(x=absample80$Whole_wgt))
sample_plot80<- sample_plot80 + geom_histogram() + labs(x="80% Sample Size")
print(sample_plot80)
sample_plot100<-ggplot(absample100, aes(x=absample100$Whole_wgt))
sample_plot100<- sample_plot100 + geom_histogram() + labs(x="100% Sample Size")
print(sample_plot100)

#creating a grid of histograms created above
require(gridExtra)
grid.arrange(sample_plot1, sample_plot10, sample_plot25, sample_plot50, sample_plot80, sample_plot100)

#Question 3

#creating variables so we can call then later in our for loop
meansample1<-numeric()
meansample10<-numeric()
meansample25<-numeric()
meansample50<-numeric()
meansample80<-numeric()

#creating for loop that takes 1000 iterations at each sample size and calculates the mean at each iteration
for (i in 1:1000) {
  iteration1<-randomSample(abalone, n*.01, FALSE)
  meansample1[[i]]<-mean(iteration1$Whole_wgt)
  
iteration10<-randomSample(abalone, n*.10, FALSE)
meansample10[[i]]<-mean(iteration10$Whole_wgt)

iteration25<-randomSample(abalone, n*.25, FALSE)
meansample25[[i]]<-mean(iteration25$Whole_wgt)

iteration50<-randomSample(abalone, n*.50, FALSE)
meansample50[[i]]<-mean(iteration50$Whole_wgt)

iteration80<-randomSample(abalone, n*.80, FALSE)
meansample80[[i]]<-mean(iteration80$Whole_wgt)

}

#putting all our variables from our for loop into a data frame that has a column for each of the sample sizes, and 1000 rows where each row is an iteration and the mean calculated at the iteration
means<-data.frame(meansample1, meansample10, meansample25, meansample50, meansample80)

dim(means)


#Question 4

 #to create grid of histograms for each of the sample sizes (except 100%)

for (i in 1:5){
mean_plot[[i]]<-ggplot(means, aes(x=means[[i]]))
mean_plot[[i]] <- mean_plot[[i]] + geom_histogram()+
  labs(x=names(means)[[i]])
}

#create a histogram for just the 100% sample i.e. the entire abalone Whole_wgt column
fullsample<-ggplot(abalone, aes(x=abalone$Whole_wgt))
fullsample<-fullsample + geom_histogram() + labs(x="100% Sample Size")

#combing all our histograms into a grid of histograms
grid.arrange(mean_plot[[1]], mean_plot[[2]], mean_plot[[3]], mean_plot[[4]], mean_plot[[5]], allmeans)



#Question 5


#calculating our minimum, maximum, mean, and variance values at each of the sample sizes
remin<-c(min(means$`meansample1`), min(means$`meansample10`), min(means$`meansample25`), min(means$`meansample50`), min(means$`meansample80`), min(abalone$Whole_wgt))

remax<-c(max(means$`meansample1`), max(means$`meansample10`), max(means$`meansample25`), max(means$`meansample50`), max(means$`meansample80`), max(abalone$Whole_wgt))

remean<-c(mean(means$`meansample1`), mean(means$`meansample10`), mean(means$`meansample25`), mean(means$`meansample50`), mean(means$`meansample80`), mean(abalone$Whole_wgt))

revar<-c(var(means$`meansample1`), var(means$`meansample10`), var(means$`meansample25`), var(means$`meansample50`), var(means$`meansample80`), var(abalone$Whole_wgt))

#creating a dataframe with our original data frame from Question 1 and row binding the 4 variables created above
data_all3<-rbind(data_all, remin, remax, remean, revar)

#naming all rows
rownames(data_all3)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance", "ResampleMinimum", "ResampleMax","ResampleMean",  "ResampleVariance")
data_all3


#Question 6

data_all3

#pulling just the SampleMean row in our data frame for each of the sample sizes
line1<-data_all3[3,1]
line10<-data_all3[3,2]
line25<-data_all3[3,3]
line50<-data_all3[3,4]
line80<-data_all3[3,5]

#creating a histogram of our full data and plotting red mean lines of our other 5 sample sizes on the histogram. Labelling each line with the mean value
finalhist<-ggplot(abalone, aes(x=abalone$Whole_wgt))
finalhist<- finalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=line1, colour='red') +
        annotate("text",x=line1,y=0,label=line1,hjust=0) + 
  geom_vline(xintercept=line10, colour='red') +
        annotate("text",x=line10,y=0,label=line10,hjust=0) + 
  geom_vline(xintercept=line25, colour='red') +
        annotate("text",x=line25,y=0,label=line25,hjust=0) + 
  geom_vline(xintercept=line50, colour='red') +
        annotate("text",x=line50,y=0,label=line50,hjust=0) + 
  geom_vline(xintercept=line80, colour='red') +
        annotate("text",x=line80,y=0,label=line80,hjust=0) 
print(finalhist)

#Question 7

#pulling just the ResampleMean row in our data frame for each of the sample sizes
reline1<-data_all3[7,1]
reline10<-data_all3[7,2]
reline25<-data_all3[7,3]
reline50<-data_all3[7,4]
reline80<-data_all3[7,5]

#creating a histogram of our full data and plotting red resamplemean lines of our other 5 sample sizes on the histogram. Labelling each line with the mean value

refinalhist<-ggplot(abalone, aes(x=abalone$Whole_wgt))
refinalhist<- refinalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=reline1, colour='red') +
        annotate("text",x=reline1,y=0,label=reline1,hjust=0) + 
  geom_vline(xintercept=reline10, colour='red') +
        annotate("text",x=reline10,y=0,label=reline10,hjust=0) + 
  geom_vline(xintercept=reline25, colour='red') +
        annotate("text",x=reline25,y=0,label=reline25,hjust=0) + 
  geom_vline(xintercept=reline50, colour='red') +
        annotate("text",x=reline50,y=0,label=reline50,hjust=0) + 
  geom_vline(xintercept=reline80, colour='red') +
        annotate("text",x=reline80,y=0,label=reline80,hjust=0) 
print(refinalhist)
```

```{r}
#Question 8

#running our code above with the diamonds$carat data. all comments above apply here as well.


#Question 1

#to pull sample from diamonds data frame

n<-nrow(diamonds)

absample1<-randomSample(diamonds, n*.01, FALSE)
absample10<-randomSample(diamonds, n*.10, FALSE)
absample25<-randomSample(diamonds, n*.25, FALSE)
absample50<-randomSample(diamonds, n*.5, FALSE)
absample80<-randomSample(diamonds, n*.80, FALSE)
absample100<-randomSample(diamonds, n, FALSE)

data1<-c(min(absample1$carat), max(absample1$carat), mean(absample1$carat), var(absample1$carat))
data10<-c(min(absample10$carat), max(absample10$carat), mean(absample10$carat), var(absample10$carat))
data25<-c(min(absample25$carat), max(absample25$carat), mean(absample25$carat), var(absample25$carat))
data50<-c(min(absample50$carat), max(absample50$carat), mean(absample50$carat), var(absample50$carat))
data80<-c(min(absample80$carat), max(absample80$carat), mean(absample80$carat), var(absample80$carat))
data100<-c(min(absample100$carat), max(absample100$carat), mean(absample100$carat), var(absample100$carat))
data_all<-data.frame(data1, data10, data25, data50, data80, data100)

colnames(data_all)<-c("1%Sample", "10%Sample", "25%Sample", "50%Sample", "80%Sample", "100%Sample")
rownames(data_all)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance")

data_all

#Question 2
require(ggplot2)


#add labels for all histograms
sample_plot1<-ggplot(absample1, aes(x=absample1$carat))
sample_plot1<- sample_plot1 + geom_histogram() + labs(x="1% Sample Size")
print(sample_plot1)
sample_plot10<-ggplot(absample10, aes(x=absample10$carat))
sample_plot10<- sample_plot10 + geom_histogram() + labs(x="10% Sample Size")
print(sample_plot10)
sample_plot25<-ggplot(absample25, aes(x=absample25$carat))
sample_plot25<- sample_plot25 + geom_histogram() + labs(x="25% Sample Size")
print(sample_plot25)
sample_plot50<-ggplot(absample50, aes(x=absample50$carat))
sample_plot50<- sample_plot50 + geom_histogram() + labs(x="50% Sample Size")
print(sample_plot50)
sample_plot80<-ggplot(absample80, aes(x=absample80$carat))
sample_plot80<- sample_plot80 + geom_histogram() + labs(x="80% Sample Size")
print(sample_plot80)
sample_plot100<-ggplot(absample100, aes(x=absample100$carat))
sample_plot100<- sample_plot100 + geom_histogram() + labs(x="100% Sample Size")
print(sample_plot100)

require(gridExtra)
grid.arrange(sample_plot1, sample_plot10, sample_plot25, sample_plot50, sample_plot80, sample_plot100)

#Question 3

meansample1<-numeric()
meansample10<-numeric()
meansample25<-numeric()
meansample50<-numeric()
meansample80<-numeric()

for (i in 1:1000) {
  iteration1<-randomSample(diamonds, n*.01, FALSE)
  meansample1[[i]]<-mean(iteration1$carat)
  
iteration10<-randomSample(diamonds, n*.10, FALSE)
meansample10[[i]]<-mean(iteration10$carat)

iteration25<-randomSample(diamonds, n*.25, FALSE)
meansample25[[i]]<-mean(iteration25$carat)

iteration50<-randomSample(diamonds, n*.50, FALSE)
meansample50[[i]]<-mean(iteration50$carat)

iteration80<-randomSample(diamonds, n*.80, FALSE)
meansample80[[i]]<-mean(iteration80$carat)

}

means<-data.frame(meansample1, meansample10, meansample25, meansample50, meansample80)

dim(means)


#Question 4

 #to create grid of histograms for each of the sample sizes (except 100%)


for (i in 1:5){
mean_plot[[i]]<-ggplot(means, aes(x=means[[i]]))
mean_plot[[i]] <- mean_plot[[i]] + geom_histogram()+
  labs(x=names(means)[[i]])
}

fullsample<-ggplot(diamonds, aes(x=diamonds$carat))
fullsample<-fullsample + geom_histogram() + labs(x="100% Sample Size")

grid.arrange(mean_plot[[1]], mean_plot[[2]], mean_plot[[3]], mean_plot[[4]], mean_plot[[5]], allmeans)



#Question 5

#calculating our minimum, maximum, mean, and variance values at each of the sample sizes
remin<-c(min(means$`meansample1`), min(means$`meansample10`), min(means$`meansample25`), min(means$`meansample50`), min(means$`meansample80`), min(diamonds$carat))

remax<-c(max(means$`meansample1`), max(means$`meansample10`), max(means$`meansample25`), max(means$`meansample50`), max(means$`meansample80`), max(diamonds$carat))

remean<-c(mean(means$`meansample1`), mean(means$`meansample10`), mean(means$`meansample25`), mean(means$`meansample50`), mean(means$`meansample80`), mean(diamonds$carat))

revar<-c(var(means$`meansample1`), var(means$`meansample10`), var(means$`meansample25`), var(means$`meansample50`), var(means$`meansample80`), var(diamonds$carat))


data_all3<-rbind(data_all, remin, remax, remean, revar)
rownames(data_all3)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance", "ResampleMinimum", "ResampleMax","ResampleMean",  "ResampleVariance")
data_all3


#Question 6

data_all3
line1<-data_all3[3,1]
line10<-data_all3[3,2]
line25<-data_all3[3,3]
line50<-data_all3[3,4]
line80<-data_all3[3,5]

finalhist<-ggplot(diamonds, aes(x=diamonds$carat))
finalhist<- finalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=line1, colour='red') +
        annotate("text",x=line1,y=0,label=line1,hjust=0) + 
  geom_vline(xintercept=line10, colour='red') +
        annotate("text",x=line10,y=0,label=line10,hjust=0) + 
  geom_vline(xintercept=line25, colour='red') +
        annotate("text",x=line25,y=0,label=line25,hjust=0) + 
  geom_vline(xintercept=line50, colour='red') +
        annotate("text",x=line50,y=0,label=line50,hjust=0) + 
  geom_vline(xintercept=line80, colour='red') +
        annotate("text",x=line80,y=0,label=line80,hjust=0) 
print(finalhist)

#Question 7

reline1<-data_all3[7,1]
reline10<-data_all3[7,2]
reline25<-data_all3[7,3]
reline50<-data_all3[7,4]
reline80<-data_all3[7,5]

refinalhist<-ggplot(diamonds, aes(x=diamonds$carat))
refinalhist<- refinalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=reline1, colour='red') +
        annotate("text",x=reline1,y=0,label=reline1,hjust=0) + 
  geom_vline(xintercept=reline10, colour='red') +
        annotate("text",x=reline10,y=0,label=reline10,hjust=0) + 
  geom_vline(xintercept=reline25, colour='red') +
        annotate("text",x=reline25,y=0,label=reline25,hjust=0) + 
  geom_vline(xintercept=reline50, colour='red') +
        annotate("text",x=reline50,y=0,label=reline50,hjust=0) + 
  geom_vline(xintercept=reline80, colour='red') +
        annotate("text",x=reline80,y=0,label=reline80,hjust=0) 
print(refinalhist)



```

```{r}

#running our code above with the faithful$eruptions data. all comments above apply here as well.

#Question 1

#to pull sample from faithful data frame

n<-nrow(faithful)

absample1<-randomSample(faithful, n*.01, FALSE)
absample10<-randomSample(faithful, n*.10, FALSE)
absample25<-randomSample(faithful, n*.25, FALSE)
absample50<-randomSample(faithful, n*.5, FALSE)
absample80<-randomSample(faithful, n*.80, FALSE)
absample100<-randomSample(faithful, n, FALSE)


data1<-c(min(absample1$eruptions), max(absample1$eruptions), mean(absample1$eruptions), var(absample1$eruptions))
data10<-c(min(absample10$eruptions), max(absample10$eruptions), mean(absample10$eruptions), var(absample10$eruptions))
data25<-c(min(absample25$eruptions), max(absample25$eruptions), mean(absample25$eruptions), var(absample25$eruptions))
data50<-c(min(absample50$eruptions), max(absample50$eruptions), mean(absample50$eruptions), var(absample50$eruptions))
data80<-c(min(absample80$eruptions), max(absample80$eruptions), mean(absample80$eruptions), var(absample80$eruptions))
data100<-c(min(absample100$eruptions), max(absample100$eruptions), mean(absample100$eruptions), var(absample100$eruptions))
data_all<-data.frame(data1, data10, data25, data50, data80, data100)

colnames(data_all)<-c("1%Sample", "10%Sample", "25%Sample", "50%Sample", "80%Sample", "100%Sample")
rownames(data_all)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance")

data_all

#Question 2
require(ggplot2)


#add labels for all histograms
sample_plot1<-ggplot(absample1, aes(x=absample1$eruptions))
sample_plot1<- sample_plot1 + geom_histogram() + labs(x="1% Sample Size")
print(sample_plot1)
sample_plot10<-ggplot(absample10, aes(x=absample10$eruptions))
sample_plot10<- sample_plot10 + geom_histogram() + labs(x="10% Sample Size")
print(sample_plot10)
sample_plot25<-ggplot(absample25, aes(x=absample25$eruptions))
sample_plot25<- sample_plot25 + geom_histogram() + labs(x="25% Sample Size")
print(sample_plot25)
sample_plot50<-ggplot(absample50, aes(x=absample50$eruptions))
sample_plot50<- sample_plot50 + geom_histogram() + labs(x="50% Sample Size")
print(sample_plot50)
sample_plot80<-ggplot(absample80, aes(x=absample80$eruptions))
sample_plot80<- sample_plot80 + geom_histogram() + labs(x="80% Sample Size")
print(sample_plot80)
sample_plot100<-ggplot(absample100, aes(x=absample100$eruptions))
sample_plot100<- sample_plot100 + geom_histogram() + labs(x="100% Sample Size")
print(sample_plot100)

require(gridExtra)
grid.arrange(sample_plot1, sample_plot10, sample_plot25, sample_plot50, sample_plot80, sample_plot100)

#Question 3

meansample1<-numeric()
meansample10<-numeric()
meansample25<-numeric()
meansample50<-numeric()
meansample80<-numeric()


for (i in 1:1000) {
  iteration1<-randomSample(faithful, n*.01, FALSE)
  meansample1[[i]]<-mean(iteration1$eruptions)
  
iteration10<-randomSample(faithful, n*.10, FALSE)
meansample10[[i]]<-mean(iteration10$eruptions)

iteration25<-randomSample(faithful, n*.25, FALSE)
meansample25[[i]]<-mean(iteration25$eruptions)

iteration50<-randomSample(faithful, n*.50, FALSE)
meansample50[[i]]<-mean(iteration50$eruptions)

iteration80<-randomSample(faithful, n*.80, FALSE)
meansample80[[i]]<-mean(iteration80$eruptions)

}

means<-data.frame(meansample1, meansample10, meansample25, meansample50, meansample80)

dim(means)


#Question 4

 #to create grid of histograms for each of the sample sizes (except 100%)


for (i in 1:5){
mean_plot[[i]]<-ggplot(means, aes(x=means[[i]]))
mean_plot[[i]] <- mean_plot[[i]] + geom_histogram()+
  labs(x=names(means)[[i]])
}

fullsample<-ggplot(faithful, aes(x=faithful$eruptions))
fullsample<-fullsample + geom_histogram() + labs(x="100% Sample Size")

grid.arrange(mean_plot[[1]], mean_plot[[2]], mean_plot[[3]], mean_plot[[4]], mean_plot[[5]], allmeans)



#Question 5

#calculating our minimum, maximum, mean, and variance values at each of the sample sizes
remin<-c(min(means$`meansample1`), min(means$`meansample10`), min(means$`meansample25`), min(means$`meansample50`), min(means$`meansample80`), min(dfaithful$eruptions))

remax<-c(max(means$`meansample1`), max(means$`meansample10`), max(means$`meansample25`), max(means$`meansample50`), max(means$`meansample80`), max(faithful$eruptions))

remean<-c(mean(means$`meansample1`), mean(means$`meansample10`), mean(means$`meansample25`), mean(means$`meansample50`), mean(means$`meansample80`), mean(faithful$eruptions))

revar<-c(var(means$`meansample1`), var(means$`meansample10`), var(means$`meansample25`), var(means$`meansample50`), var(means$`meansample80`), var(faithful$eruptions))


data_all3<-rbind(data_all, remin, remax, remean, revar)
rownames(data_all3)<-c("SampleMinimum", "SampleMaximum", "SampleMean", "SampleVariance", "ResampleMinimum", "ResampleMax","ResampleMean",  "ResampleVariance")
data_all3


#Question 6

data_all3
line1<-data_all3[3,1]
line10<-data_all3[3,2]
line25<-data_all3[3,3]
line50<-data_all3[3,4]
line80<-data_all3[3,5]

finalhist<-ggplot(faithful, aes(x=faithful$eruptions))
finalhist<- finalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=line1, colour='red') +
        annotate("text",x=line1,y=0,label=line1,hjust=0) + 
  geom_vline(xintercept=line10, colour='red') +
        annotate("text",x=line10,y=0,label=line10,hjust=0) + 
  geom_vline(xintercept=line25, colour='red') +
        annotate("text",x=line25,y=0,label=line25,hjust=0) + 
  geom_vline(xintercept=line50, colour='red') +
        annotate("text",x=line50,y=0,label=line50,hjust=0) + 
  geom_vline(xintercept=line80, colour='red') +
        annotate("text",x=line80,y=0,label=line80,hjust=0) 
print(finalhist)

#Question 7

reline1<-data_all3[7,1]
reline10<-data_all3[7,2]
reline25<-data_all3[7,3]
reline50<-data_all3[7,4]
reline80<-data_all3[7,5]

refinalhist<-ggplot(faithful, aes(x=faithful$eruptions))
refinalhist<- refinalhist + geom_histogram() + labs(x="100% Data") + geom_vline(xintercept=reline1, colour='red') +
        annotate("text",x=reline1,y=0,label=reline1,hjust=0) + 
  geom_vline(xintercept=reline10, colour='red') +
        annotate("text",x=reline10,y=0,label=reline10,hjust=0) + 
  geom_vline(xintercept=reline25, colour='red') +
        annotate("text",x=reline25,y=0,label=reline25,hjust=0) + 
  geom_vline(xintercept=reline50, colour='red') +
        annotate("text",x=reline50,y=0,label=reline50,hjust=0) + 
  geom_vline(xintercept=reline80, colour='red') +
        annotate("text",x=reline80,y=0,label=reline80,hjust=0) 
print(refinalhist)

```

```{r}
#Question 9

#Mean values seem to be similar for our sample sizes whether whether we take the sample mean or resample the mean for each of the sample sizes. We see this for the abalone and diamonds data sets, but notice a difference in the re-sample histogram for the faithful dataframe. This could be due to the small sample size in faithful (272) as compared to abalone (4176) and diamonds(53940).

dim(faithful)
dim(diamonds)
dim(abalone)
